\section{Board of Directors}
\label{sec:directors}

\subsection{Number of Directors}

Except for the initial Board named in the Articles of Incorporation,
the Board of Directors shall consist of twelve (12) Directors.

\subsection{Composition of the Board}

There shall be three categories of Directors, each consisting of four
Directors, or one third of the total Board. The three categories shall
be ``Lessee Representatives'' representing Lessee Members, ``General
Representatives'' representing General Members, and ``Public
Representatives'' representing the interests of the general public.

\subsection{Nomination of Directors}

For all regular elections subsequent to the first Annual Meeting of
the Membership, Directors shall be nominated as follows:
\begin{enumerate}[a.]
\item \emph{Lessee Representatives.}
  \begin{enumerate}[(1)]
  \item Lessee Members may nominate Lessee Representatives to the
    Board from among themselves. These nominations must either be
    submitted in writing to the Secretary of the Corporation at least
    ten days prior to the Annual Membership Meeting or be made from
    the floor at the Annual Meeting.
  \item In the event that, at the time when the notice of the Annual
    Membership Meeting is to be sent out, the number of nominations is
    less than the number of Lessee Representative seats to be filled,
    the Board of Directors shall nominate enough candidates so that
    the total number of candidates is sufficient to fill the number of
    seats to be filled. To achieve this end, the Board may, at any
    time prior to the sending out of such notice, approve a list of
    candidates for Lessee Representative to be nominated in such
    event. In making such nominations, the Board shall select actual
    Lessees to the extent that they are available to serve on the
    Board of Directors. Otherwise the Board shall select persons who
    can reasonably be expected to represent the normal interests and
    concerns of Lessees.
  \end{enumerate}
\item{General Representatives.}
  \begin{enumerate}[(1)]
  \item General Members may nominate General Representatives to the
    Board from among themselves. These nominations must either be
    submitted in writing to the Secretary of the Corporation at least
    ten days prior to the Annual Meeting or be made from the floor at
    the Annual Meeting.
  \item If, at the time the notice of the Annual Membership Meeting is
    to be sent out, the number of nominations for General
    representative is less than the number of General Representative
    seats to be filled, the Board of Directors shall nominate enough
    candidates so that the total number of candidates is sufficient to
    fill the number of seats to be filled. To achieve this end, the
    Board may, at any time prior to the sending out of such notice,
    approve a list of candidates for General Representatives to be
    nominated in such event.
  \end{enumerate}
\item \emph{Public Representatives.}  At least ten days prior to the
  Annual Meeting, the Board of Directors shall make nominations for
  Public Representatives to the Board.
\item \emph{Notice of Nominations.}  A list of all persons nominated
  in each of the three categories shall be included with the notice of
  the Annual Meeting.
\end{enumerate}

\subsection{Election of Directors}
Directors shall be elected by the Regular Members present and voting
at the Annual Meeting, a quorum being assembled, in accordance with
the following procedures.
\begin{enumerate}[a.]
\item A separate vote shall be taken for each of the three categories
  of Board representatives: (1) Lessee Representatives, (2) General
  Representatives, and (3) Public Representatives. If a person has
  been nominated in more than one category and is then elected in one
  category, his or her name shall be removed from the list of nominees
  in the remaining categories.
\item Only Lessee Members may vote to elect Lessee Representatives
  unless no Lessee members are present at the Annual Membership
  Meeting. If no Lessee members are present, then General Members may
  vote to elect Lessee Representatives. Each Member qualified to vote
  for Lessee Representatives may cast a Single Transferable Vote by a
  ballot of ranked-choice preferences.
\item Only General Members may vote to elect General Representatives
  unless no General members are present at the Annual Membership
  Meeting. If no General Members are present, then Lessee Members may
  vote to elect General Representatives. Each Member qualified to vote
  for General Representatives may cast a Single Transferable Vote by a
  ballot of ranked-choice preferences.
\item All Regular Members (both Lessee and General Members) may vote
  to elect Public Representatives. Each Regular Member may cast a
  Single Transferable Vote by a ballot of ranked-choice preferences.
\item In each of the three categories separately, candidates receiving
  votes totalling at least the quota, one more than the ratio of the
  total number of votes divided by one more than the number of
  vacancies, shall be declared provisionally-elected. While the
  vacancies outnumber the provisionally-elected candidates, each
  provisionally-elected candidate’s votes in excess of the quota is
  redistributed proportionally to the next choice on each of the
  corresponding ballots, in order of greatest excess. If there remain
  more candidates than vacancies, and more vacancies than
  provisionally-elected candidates, the process is repeated with the
  exclusion of the least-supported candidate. Ties will be broken by
  the toss of a coin.
\end{enumerate}

\subsection{Vacancies}
\begin{enumerate}[a.]
\item If any Director vacates his or her term or is removed from the
  Board, the remaining Directors (though they may constitute less than
  a quorum) may elect a person to fill the vacancy, or may, by
  unanimous agreement, decide to leave the position vacant until the
  next Annual Meeting of the Membership, provided the Board still
  includes at least three Representatives in each category. Elections
  to fill vacancies shall be by a majority of the remaining Directors.
\item Any person elected to fill a vacancy on the Board of Directors
  must be one who can be reasonably expected to represent the
  interests of the constituents in the category (Lessee, General, or
  Public) in which the vacancy occurs.
\item Replacement Directors elected by the Board shall serve out the
  remaining term of the person who has vacated the position.
\end{enumerate}

\subsection{Low-Income Representation}
In their actions regarding the nomination and election of directors
and appointment of people to fill vacancies on the Board of Directors,
the membership and the board of directors shall at all times ensure
that at least one third of the Board is maintained for residents of
low-income neighborhoods, other low-income community residents, or
representatives of low-income neighborhood organization.

\subsection{Terms of Directors}
\begin{enumerate}[a.]
\item \emph{Terms of First Elected Directors.}  After the election of
  Directors at the first Annual Meeting, each Director shall be
  assigned, by mutual agreement or by lot, to a one-year or two-year
  term. In each of the three categories of Representatives, two
  Directors shall be assigned a one-year term and two shall be
  assigned a two-year term.
\item \emph{Terms of Successor Directors.}  Except as otherwise
  provided in these Bylaws, each Director shall serve a full term of
  two years.
\item \emph{Commencement of Terms.}  The term of office of a regularly
  elected Director shall commence at the adjournment of the Annual
  Membership Meeting in which he or she is elected. The term of office
  of a Director elected by the Board to fill a vacancy shall begin at
  the time of his or her acceptance of the position.
\item \emph{Re-election.}  No person shall serve as a Director for
  more than three consecutive elected terms. After a year’s absence
  from the Board, however, a person who has served three consecutive
  elected terms may return to the Board, if re-elected, and may serve
  up to three consecutive elected terms.
\end{enumerate}
  
\subsection{Resignation}
\begin{enumerate}[a.]
\item Any Director may resign at any time by giving written notice to
  the President. Unless otherwise specified, such resignation shall be
  effective upon the receipt of notice by the President
\item A Director shall be considered to have given notice of
  resignation and his or her position shall be declared vacant by the
  Board of Directors if he or she fails to attend three consecutive
  meetings of the Board with the exception of emergency meetings,
  unless good cause for absence and continuing interest in
  participation on the Board are recognized by the Board. When a
  Director has failed to attend three consecutive meetings, the
  President shall notify him or her in writing that, at the next
  regular Board meeting, his or her position will be declared vacant
  unless the Board determines that there has been good cause for the
  Director’s absences and that the Director continues to be interested
  in participating on the Board of Directors. The notification by the
  President shall be mailed no later than seven days prior to the
  Board meeting at which the position may be declared vacant. At this
  meeting, the Director in question shall be given the opportunity to
  show good cause for past absences from meetings and continuing
  interest in participating on the Board. The resignation of a
  Director who has missed three consecutive meetings shall not become
  effective until the Board has declared the position vacant as
  provided herein.
\end{enumerate}

\subsection{Removal of Directors}
A Director of the Corporation may be removed for good cause by the
regular members of the Corporation when such Director is judged to
have acted in a manner seriously detrimental to the
Corporation. However, before such removal can occur, the following
procedure must be followed.
\begin{enumerate}[a.]
\item Written charges specifying the conduct considered to be
  detrimental must be signed by at least three members of the
  Corporation and submitted to the President (or, if the President is
  the Director charged, to the Vice President). Any Regular Members of
  the Corporation may submit such charges.
\item The President (or Vice President) shall deliver or mail a copy
  of the charges to the Director charged.
\item A Special Committee consisting of three Regular Members of the
  Corporation shall be created to consider the charges. One member of
  the Committee shall be selected by the Board of Directors, but
  without the participation of the Director charged, within ten days
  following the delivery or mailing of the charges to the Director
  charged. In making its selection, the Board shall endeavor to select
  a person who will consider the charges without bias. No later than
  ten days following the Board’s selection of the first member of the
  Committee, a second member may be selected by the Director
  charged. In the event that the Director charged fails to select a
  second member of the Committee within ten days, the Board may select
  a second member who, in the judgement of the Board, will consider
  the charges without bias. Within ten days following the selection of
  the second member of the Committee, the first and second members
  shall select a third member of the Committee. If the first and
  second members cannot agree upon a third member within this ten-day
  period, the Board shall select a third member.
\item The Special Committee shall hold a hearing, at which both the
  Director charged and the members who have filed charges may present
  evidence in the presence of the other. Following the hearing, the
  Committee shall prepare a written report of its findings and its
  recommendation for or against removal. The recommendation shall be
  based on a majority vote if consensus cannot be reached. The report
  shall contain a statement of how each member of the Committee has
  voted. The report shall be completed and submitted to the President
  of the Corporation no later than one month following the selection
  of the third member of the Committee.
\item If the Committee recommends removal of the Director, the
  recommendation shall be presented to the Regular Membership, which
  shall then have sole authority to decide the question of removal. A
  Membership meeting for this purpose shall be called by the President
  for a time no later than one month following the President’s receipt
  of the Committee’s recommendation for removal. Notice of this
  meeting shall include a complete copy of the Committee’s report.
\end{enumerate}

\subsection{Meetings of the Board of Directors}
\begin{enumerate}[a.]
\item \emph{Notice of Meetings.}  Except as provided below for
  emergency meetings, written notice of a Board meeting shall be sent
  by first class mail to all Directors at least seven days prior to
  the meeting, or shall be delivered in person or emailed at least
  five days prior to the meeting, provided that Directors must opt-in
  to receipt of notice by email by providing prior written notice to
  the Secretary of such election. Notice of every meeting shall
  include an agenda for the meeting.
\item \emph{Waiver of Notice.}  Any Director may waive any notice
  required by these Bylaws. Any Director who has not received notice
  of a Board meeting but has attended that meeting shall be considered
  to have waived notice of that meeting, unless he or she requests
  that his or her protest be recorded in the minutes of the meeting.
\item \emph{Annual Meeting.} The Annual Meeting of the Board of
  Directors may be held immediately following the Annual Membership
  Meeting and must be held no later than six weeks following the
  Annual Membership Meeting.
\item \emph{Regular Meetings.}  The Board of Directors shall meet no
  less often than once every two months, at such times and places as
  the Board may establish.
\item \emph{Special Meetings and Emergency Meetings.}  Special
  meetings may be called by the President, by any three Directors, or
  by 10\% of the Regular Members of the Corporation. Notice must be
  given as provided above, unless any three Directors determine that
  the matter at hand constitutes an emergency. When so determined, an
  Emergency Meeting may be called on one-day notice. Notice of
  Emergency Meetings, including an announcement of the agenda, shall
  be given by telephone or in person to all Directors. At any Special
  or Emergency Meeting of the Board, only those matters included in
  the announced agenda may be acted upon unless all of the Directors
  are present at the meeting and unanimously agree to take action on
  other matters.
\end{enumerate}
  
\subsection{Procedures for Meetings of the Board of Directors}
\begin{enumerate}[a.]
\item \emph{Open Meetings.}  All meetings of the Board of Directors
  shall be open to any person except when the Board has voted, during
  an open meeting, to go into executive session.
\item \emph{Executive Session.}  A motion to go into executive session
  shall state the nature of the business of the executive session, and
  no other matter may be considered in the executive session. No
  binding action may be taken in executive session except actions
  regarding the securing of real estate purchase options or contracts
  in accordance with paragraph b-2 below. Attendance in executive
  session shall be limited to the Directors and any persons whose
  presence is requested by the Board of Directors. Minutes of an
  executive session need not be taken; however, if they are taken,
  they shall be recorded as a part of the minutes of the meeting in
  which the Board has voted to go into executive session. The Board
  shall not hold an executive session except to consider one or more
  of the following matters.
  \begin{enumerate}[(1)]
  \item Contracts, labor relations agreements with employees,
    arbitration, grievances, or litigation involving the Corporation
    when premature public knowledge would place the Corporation or
    person involved at a substantial disadvantage.
  \item Real estate purchase offers and the negotiating or securing of
    real estate purchase options or contracts.
  \item The appointment or evaluation of an employee, and any
    disciplinary or dismissal action against an employee (however,
    nothing in this section shall be construed to impair the right of
    the employee to a public hearing if action is taken to discipline
    or dismiss).
  \item The consideration of applications from persons seeking to
    lease land and/or housing, purchase housing or other improvements,
    or arrange financing from the Corporation.
  \item Relationships between the Corporation and any party who might
    be harmed by public discussion of matters relating to the
    relationship.
  \end{enumerate}
\item \emph{Quorum.}  At any meeting of the Board, a quorum shall
  consist of a majority of the Board of Directors, provided that at
  least one representative from each of the three categories of
  representatives is present.
\item \emph{Decision-Making.}  The Board shall attempt to reach
  unanimous agreement on all decisions. In the event that unanimous
  agreement cannot be achieved, a decision may be made by a majority
  of the Directors present and voting, except as otherwise provided in
  these Bylaws.
\item \emph{Minutes.}  Minutes of all Board meetings shall be recorded
  by the Secretary or by such other person as the Board may designate,
  and shall be corrected as necessary and approved by the Board at the
  next Board meeting. All duly approved minutes of Board meetings
  shall be kept on permanent record by the Corporation and shall be
  open for inspection by any Member of the Corporation.
\end{enumerate}
  
\subsection{Duties of the Board of Directors}

The Board of Directors shall carry out the purposes of the
Corporation, implement the decisions of the Regular Membership, and be
responsible for the general management of the affairs of the
Corporation in accordance with these Bylaws. Specifically, the Board
shall:
\begin{enumerate}[a.]
\item Approve a written Annual Report to The Membership, and make this
  report available to all members. This report shall include a summary
  of the Corporation’s activities during the previous year, the
  Corporation’s most recent financial reports, and a list of all real
  estate held by the Corporation.
\item Adopt an annual operating budget prior to the beginning of each
  fiscal year, and approve any expenditures not included in the
  budget.
\item Select all officers of the Corporation.
\item Supervise the activities of all officers, agents, and committees
  of the Corporation in the performance of their assigned duties and
  investigate any possible conflicts of interest within the
  Corporation.
\item Adopt and implement personnel policies providing for the hiring,
  supervision, and evaluation of employees.
\item Provide for the deposit of funds in accordance with Article IX
  of these Bylaws.
\item Determine by whom and in what manner deeds, leases, contracts,
  checks, drafts, endorsements, notes and other instruments shall be
  signed on behalf of the Corporation.
\item Acquire such parcels of land, with or without buildings and
  other improvements, through donation, purchase, or otherwise, as the
  Board shall determine that it is useful and prudent to acquire in
  furtherance of the purposes of the Corporation.
\item Convey the right to use land, through leases or other limited
  conveyances, in accordance with the provisions of Articles V and VI
  of these Bylaws.
\item Convey ownership of housing and other improvements on the
  Corporation’s land to qualified lessees, as possible, in accordance with the
  provisions of Articles V and VI of these Bylaws.
\item Exercise, as appropriate, the Corporation’s option to repurchase
  (or arrange for the resale of) housing and other improvements on the
  Corporation’s land, or condominium units on which the corporation
  holds a purchase option.
\item Develop the resources necessary for the operation of the
  Corporation and for the acquisition and development of land and
  housing.
\item Assure the sound management of the Corporation’s finances.
\end{enumerate}

\subsection{Powers of the Board of Directors}
In addition to the power to carry out the duties enumerated above, the
Board of Directors shall have the power to:
\begin{enumerate}[a.]
\item Appoint and discharge advisors and consultants.
\item Create such committees as are necessary or desirable to further
  the purposes of the Corporation. (Any member of the Corporation may
  be appointed to any committee. No committee may take action on
  behalf of the Corporation except as authorized by the Board of
  Directors.)
\item Call special meetings of the membership.
\item Approve the borrowing and lending of money as necessary to
  further the purposes of the Corporation and in accordance with
  paragraph IX-4 of these Bylaws.
\item Exercise all other powers necessary to conduct the affairs and
  further the purposes of the Corporation in accordance with the
  Certificate of Incorporation and these Bylaws.
\end{enumerate}


\subsection{Limitation on the Powers of the Board of Directors}
Action taken by the Board of Directors on any motion for the
assessment of membership dues, the removal of Directors, the sale of
land, the establishment or alteration of the “resale formula,” the
amendment of the Certificate of Incorporation or these Bylaws, or
dissolution of the Corporation shall not become effective unless and
until such action is approved by the Regular Membership in accordance
with these Bylaws.

