\section{Initial Membership and Board, Adoption of Bylaws, First Annual Meeting}

\subsection{Initial Membership}
The Initial Members empowered to vote at the first annual meeting
shall be those persons 18 years of age or older who have attended at
least one of the organizational meetings held between May 1, 2016, and
the time of the First Annual Meeting, as recorded in the minutes of
these meetings.

\subsection{Initial Board of Directors}
The Initial Board of Directors shall be as stated in the Certificate
of Incorporation. The Initial Board, after approving these Bylaws,
shall call the first Annual Meeting of the Membership, and shall serve
until the first elected Board of Directors has been seated upon the
completion of the First Annual Meeting.

\subsection{Adoption of Bylaws}
Adoption of these Bylaws as the Bylaws of the Corporation shall
require:
\begin{enumerate}[a.]
  \item Approval by a majority of the Initial Board of Directors prior
    to the First Annual Meeting; and
  \item Ratification by two thirds of the Initial Members present and
    voting at the First Annual Meeting.
\end{enumerate}

\subsection{Nomination of Directors to Be Elected at First Annual Meeting}
In consultation with the Initial Board of Directors, the Members shall
nominate a slate of candidates, and shall designate four of these
candidates as candidates for “Lessee Representatives,” four as
candidates for “General Representatives,” and four as candidates for
“Public Representatives.” Additional nominations for any of the three
categories of representatives may be made by any Initial Member from
the floor at the First Annual Meeting.

\subsection{First Annual Meeting}
The location and specific time of the First Annual Meeting of the
Membership shall be determined by the Initial Board of
Directors. Notice of the First Annual meeting shall be mailed to all
Initial Members at least seven days prior to the Meeting and shall
include a list of those persons nominated for the Board of Directors
in accordance with Paragraph 4 above. Except as otherwise provided in
this Article, the election of Directors and other business of the
First Annual Meeting shall be conducted in accordance with
\ref{sec:membership} and \ref{sec:directors} of these Bylaws.

