\section{Membership}
\label{sec:membership}

\subsection{Regular Membership}
Subsequent to the first annual meeting, the Regular Members of the
Corporation, with full voting rights, shall be:
\begin{enumerate}[a.]
\item The Lessee Members, who shall be all persons who lease land or
  housing from the Corporation or who lease or own housing that is
  located on land leased by another entity from the Corporation.
\item The General Members, who shall be all other persons, eighteen
  years of age or older, and residing within the City of Rochester,
  NY, who have:
  \begin{enumerate}[(1)]
  \item Submitted a Membership application including a signed
    statement of support for the purposes of the Corporation in a form
    to be determined by the Board of Directors, and
  \item Fulfilled at least two of the following three criteria:
    \begin{enumerate}[i.]
      \item Payment of dues as established by the Membership for the
        current calendar year.
      \item Attendance at a minimum of 4 of the Corporation's
        planning/committee meetings since the last Annual Meeting or
        within the past 12 months.
      \item Volunteer service on behalf of the Corporation at a
        presentation, tabling event, or similar, since the last Annual
        Meeting or within the past 12 months.
    \end{enumerate}
  \end{enumerate}
\end{enumerate}

\subsection{Requirements for Continuing Regular Membership}
To maintain Regular Membership beyond a person’s first year of Regular
Membership a person must either be a Lessee Member or have met the
General Membership requirements outlined above while continuing to
reside within the City of Rochester, NY.

\subsection{Membership Dues}
\begin{enumerate}[a.]
\item Annual membership dues shall be assessed for each calendar year
  by an affirmative vote of a majority of the Regular Members present
  and voting at the Annual Meeting preceding that year. If no such
  action is taken to assess dues for a given year, the dues for that
  year shall be as established for the previous year.
\item Annual dues may be paid either in cash or through a contribution
  of labor to the organization at prevailing wage rates. The Board of
  Directors shall determine the hourly rate at which labor will be
  credited as dues, and shall have the power to designate the types of
  labor that may be credited.
\end{enumerate}
  
\subsection{Rights of Regular Members}
\begin{enumerate}[a.]
\item Every Regular Member shall have the right to participate in
  meetings of the Membership, to cast one vote on all matters properly
  put before the Membership for consideration, to nominate and
  participate in the election of the Board of Directors as provided by
  these Bylaws, to serve on the Board of Directors or on committees if
  chosen, and to receive notices and minutes of Membership Meetings
  and Annual Reports of the Corporation.
\item The assent of the Regular Membership, in accordance with these
  Bylaws, shall be required before action may be taken on the
  assessment of membership dues, the sale of land, the establishment
  or alteration of limitations on rent and resale, the amendment of
  the Certificate of Incorporation or these Bylaws, and the
  dissolution of the Corporation.
\end{enumerate}
  
\subsection{Supporting Membership}
\begin{enumerate}[a.]
\item Any person who has paid the annual dues established for the
  current calendar year but who does not wish to become a Regular
  Member or has not met all of the requirements of Regular Membership
  shall be designated a Supporting Member of the Corporation.
\item Supporting Members shall have all of the rights of Regular
  Members except the right to nominate and participate in the election
  of the Board of Directors and the right to vote on matters put
  before the Regular Membership.
\end{enumerate}

\subsection{Membership Meetings}
\begin{enumerate}[a.]
\item \emph{Notice of Meetings.}  Written notice of every Membership
  Meeting shall be given to all Regular and Supporting Members and
  shall include an agenda for the meeting. Except as otherwise
  provided in \ref{sec:dissolution} of these Bylaws, notice shall be
  sent by first class mail or emailed at least seven days prior to a
  meeting or, provided that Members must opt-in to receipt of notice
  by email by providing prior written notice to the Secretary of such
  election.
\item \emph{Annual Meetings.}  Subsequent to the First Annual Meeting,
  the Annual Meeting of the Membership, for reports to the Membership
  by the Board of Directors and Officers, the election of Directors,
  the assessment of dues, and the transaction of other business, shall
  be held in the first quarter of each year. The location and
  specific time of the Annual Meeting shall be determined by the Board
  of Directors. Notice of the Annual Meeting shall include a list of
  those persons nominated for the Board of Directors as provided in
  \ref{sec:directors} of these Bylaws.
\item \emph{Regular Meetings.}  Regular Meetings may be scheduled by
  the Regular Membership at such times and places as they shall
  establish at the Annual Meeting.
\item \emph{Special Meetings.}  Special Membership Meetings may be
  called by the Board of Directors or by a written petition, addressed
  to the President of the Corporation, signed by at least one tenth
  (10\%) of the Regular Membership. At a Special Meeting, only those
  matters stated on the agenda, as included in the notice of the
  meeting, may be acted upon by the Membership.
\item \emph{Open meetings.}  All Membership Meetings shall be open to
  any person.
\item \emph{Minutes.}  Minutes of all Membership Meetings shall be
  recorded by the Secretary of the Corporation or by another person
  designated by the Board of Directors. Minutes for every meeting
  shall be approved by the Regular Membership at the next Membership
  Meeting.
\item \emph{Quorum.}  A quorum shall consist of at least fifty percent
  (50\%) of the total Regular Membership, as determined by the
  Secretary of the Corporation.
\item \emph{Decision-Making.} Whenever possible, decisions shall be made
at Membership Meetings by the consensus of the Regular Members
present, a quorum being assembled. Absent consensus, binary decisions
shall be made by an affirmative vote of a majority of the Regular
Members present and voting, a quorum being assembled, and non-binary
decisions shall be made by each such Member casting a Single
Transferable Vote using a ballot of ranked-choice preferences, except
as otherwise provided in these Bylaws. Before a vote is held on any
motion, the exact language of the motion shall be recorded by the
Secretary and read to the Membership, and all Members present shall
have a reasonable opportunity to express their opinions on the
proposition.
\end{enumerate}
