\section{Miscellaneous Provisions}

\subsection{Fiscal Year}
The fiscal year of the Corporation shall begin on January 1 of each
year, and shall end on December 31 of each year.

\subsection{Deposit of Funds}
All funds of the Corporation not otherwise employed shall be deposited
in such banks, trust companies, or other reliable depositories as the
Board of Directors from time to time may determine.

\subsection{Checks, etc.}
All checks, drafts, endorsements, notes and evidences of indebtedness
of the Corporation shall be signed by such officers or agents of the
Corporation and in such manner as the Board of Directors from time to
time may determine. Endorsements for deposits to the credit of the
Corporation shall be made in such manner as the Board of Directors
from time to time may determine.

\subsection{Loans}
No loans or advances shall be contracted on behalf of the Corporation,
and no note or other evidence of indebtedness shall be issued in its
name, except as authorized by the Board of Directors. Any such
authorization shall relate to specific transactions.

\subsection{Contracts}
Any officer or agent of the Corporation specifically authorized by the
Board of Directors may, on behalf of the Corporation, enter into those
contracts or execute and deliver those instruments that are
specifically authorized by the Board of Directors. Without the express
and specific authorization of the Board of Directors, no officer or
other agent of the Corporation may enter into any contract or execute
and deliver any instrument in the name of the Corporation.

\subsection{Indemnification}
Any person (and the heirs, executors and administrators of such
person) made or threatened to be made a party to any action, suit or
proceeding by reason of the fact that he or she is or was a Director
or Officer of the Corporation shall be indemnified by the Corporation
against any and all liability and the reasonable expenses, including
attorneys’ fees and disbursements, incurred by him or her (or his or
her heirs, executors, or administrators) in connection with the
defense or settlement of such action, suit, or proceeding, or in
connection with any appearance therein, except in relation to matters
as to which it shall be adjudged in such action, suit or proceeding
that such Director or Officer is liable for negligence or misconduct
in the performance of his or her duties.

