\section{Officers}

\subsection{Designation}
The officers of the Corporation shall be: President, Vice President,
Secretary, and Treasurer.

\subsection{Election}
The officers of the Corporation shall be elected by a majority vote of
the Board of Directors, from among themselves, at the Annual Meeting
of the Board. Any vacancies occurring in any of these offices shall be
filled by the Board for the unexpired term.

\subsection{Tenure}
The officers shall hold office until the next Annual Meeting of the
Board after their election, unless, before such time, they resign or
are removed from their offices, or unless they resign or are removed
from the Board of Directors. Any officer who ceases to be a member of
the Board of Directors shall thereby cease to be an officer.


\subsection{Removal from Office}
The officers shall serve at the pleasure of the Board of Directors and
may be removed from office at any time by an affirmative vote of two
thirds of the entire Board of Directors.

\subsection{Duties of the President}
The President shall:
\begin{enumerate}[a.]
\item Preside at all meetings of the Board of Directors and the
  Membership when able to do so.
\item Consult with the other officers and the committees of the
  Corporation regarding the fulfillment of their duties.
\item Assure that an agenda is prepared for every meeting of the
  Membership and the Board of Directors.
\item Give notice to any Director who has been absent from three
  consecutive regular meetings, as required by these Bylaws.
\item Call special meetings of the Membership or Board of Directors
  when petitioned to do so in accordance with these Bylaws.
\item Carry out the duties assigned to the President regarding the
  removal of a Director.
\item Perform such other duties as the Board of Directors may assign.
\end{enumerate}

\subsection{Duties of the Vice President}
The Vice President shall:
\begin{enumerate}[a.]
\item Perform all duties of the President in the event that the
  President is absent or unable to perform these duties.
\item Perform those duties assigned to the President regarding the
  resignation or removal of a Director when the President is
  disqualified from performing these duties.
\item Assure that up-to-date copies of these Bylaws (incorporating any
  duly approved amendments) are maintained by the Corporation; answer
  all questions from the Board regarding these Bylaws; and assure that
  all actions of the Membership and Board of Directors comply with
  these Bylaws.
\item Assure that any and all committees established by the board of
  directors are constituted as the board has directed and meet as
  necessary and appropriate.
\item Perform such other duties as the Board of Directors may assign.
\end{enumerate}

\subsection{Duties of the Secretary}
The Secretary shall:
\begin{enumerate}[a.]
\item Assure that a list of all Members and their mailing addresses is
  maintained by the Corporation.
\item Assure that proper notice of all meetings of the Membership and
  the Board of Directors is given.
\item Assure that motions and votes in meetings of the Membership and
  Board are accurately represented to those present and are accurately
  recorded in the minutes.
\item Assure that minutes of all meetings of the Membership and the
  Board of Directors are recorded and kept on permanent record.
\item Assure that all deeds, title papers, leases, and other documents
  establishing the Corporation's interest in property and rights in
  particular matters are systematically and securely maintained.
\item Perform such other duties as the Board of Directors may assign.
\end{enumerate}

\subsection{Duties of the Treasurer}
The Treasurer shall oversee the finances of the
Corporation. Specifically, the Treasurer shall:
\begin{enumerate}[a.]
\item Assure that the financial records of the Corporation are
  maintained in accordance with sound accounting practices.
\item Assure that funds of the Corporation are deposited in the name
  of the Corporation in accordance with these Bylaws.
\item Assure that all money owed to the Corporation is duly collected
  and that all gifts of money or property to the Corporation are duly
  received.
\item Assure the proper disbursement of such funds as the Board of
  Directors may order or authorize to be disbursed.
\item Assure that accurate financial reports (including balance sheets
  and revenue and expense statements) are prepared and presented to
  the Board at the close of each quarter of each fiscal year.
\item Assure that such reports and returns as may be required by
  various government agencies are prepared and filed in a timely
  manner.
\item Assure that an annual operating budget is prepared and presented
  to the Board for its approval prior to the beginning of each fiscal
  year.
\end{enumerate}

