\section{Ownership of Housing and Other Improvements Located on the Corporation's Land, and Limitations on Rent and Resale}

\subsection{Ownership of Housing and Improvements on the Corporation's Land}
In accordance with the purposes of the Corporation, the Board of
Directors shall take appropriate measures to promote and facilitate
the ownership of housing and other improvements on the Corporation's
land by low and moderate income people. These measures may include,
but are not limited to, provisions for the sale of housing to such
people; provisions for financing the acquisition of housing by such
people, including direct loans by the Corporation; and provision for
grants or other subsidies that will lower the cost of housing for such
people.

\subsection{Preservation of Affordability}
It is a purpose of the Corporation to preserve the affordability of
housing and other improvements for low and moderate income people in
the future. Accordingly, when land is leased for such purpose, the
Board of Directors shall assure that, as a condition of the lease,
housing on the land may be resold only to the Corporation or to
another low or moderate income person and only for a price limited by
a “resale formula” as described in Section 3 below. The Board of
Directors shall also assure that, as a condition of the lease, housing
on the land may be rented only to low or moderate income persons and
only for an amount limited by a “rent formula”, as described in
Section 3 below. However, notwithstanding the foregoing, the Board of
Directors may choose, for reasons consistent with the charitable
purposes of the Corporation, to lease certain parcels of land for uses
that do not require continued affordability for low or moderate income
people, and in such cases the restrictions described above shall not
be required as a condition of the lease.

\subsection{Limitations on Rent and Resale}
Whenever its purpose is to preserve affordability, the Corporation
shall restrict the price that ground lessees may receive when they
rent or sell housing and other improvements located on the land that
is leased to them by the Corporation. The same policy shall be applied
in the case of condominium units stewarded by the Corporation,
regardless of whether the land is owned by the Corporation. Policies
establishing such restrictions in the forms of a ``rent formula'' and
a ``resale formula'' shall be adopted by the Board of Directors and
the Regular Members of the Corporation, in accordance with the
following principles:
\begin{enumerate}[a.]
\item To the extent possible, each formula shall allow the owner to
  receive a price based on the value that the owner has actually
  invested in the property being rented or sold.
\item To the extent possible, each formula shall limit the rental or
  sale price of the property to an amount that will be affordable for
  low and moderate income people at the time of the signing of a
  rental lease or the transfer of ownership.
\end{enumerate}

\subsection{Procedures for Adoption of Limitations on Rent and Resale}
The adoption of a rent or resale formula shall require:
\begin{enumerate}[a.]
\item An affirmative vote by at least two thirds of the entire Board
  of Directors at any regular or special Board meeting, provided that
  written notice of such meeting has set forth the proposed formula
  with an explanation thereof; and
\item An affirmative vote by at least two thirds of the Regular
  Members present at any regular or special Membership meeting, a
  quorum being assembled, provided that written notice of such meeting
  has set forth the proposed formula with an explanation thereof.
\end{enumerate}

\subsection{Procedures for Altering the Limitations on Rent and Resale}
The consistent long-term application of rent and resale formulas is
essential to the purposes of the Corporation. Accordingly, the
formulas shall not be altered unless the Board of Directors and
Regular Members of the Corporation determine that the current formulas
present an obstacle to the achievement of the purposes of the
Corporation. In such event, each formula may be altered only by a
two-thirds vote of the entire Board of Directors and a two-thirds vote
of the Regular Members present at a Membership meeting, as described
above for the adoption of the formulas.

