\section{Stewardship of Land}

\subsection{Principles of Land Use}
The Board of Directors shall oversee the use of land owned by the
Corporation and shall convey the right to use such land so as to
facilitate access to land and affordable housing by low and moderate
income people. In so doing, the Board shall be guided by the following
principles:
\begin{enumerate}[a.]
\item The Board shall consider the needs of potential lessees.
\item The Board shall convey land use rights on terms that will
  preserve affordable access to land and housing for future low and
  moderate income residents of the community.
\item The Board shall convey land use rights in a manner that will
  promote the long-term well-being of the community and the long-term
  health of the environment.
\end{enumerate}

\subsection{Encumbrance of Land}
The decision to mortgage or otherwise encumber land owned by the
Corporation shall require the approval of the Board of Directors. Any
such encumbrance shall be subordinated to any ground leases relating
to such land.

\subsection{Sale of Land}
The sale of land does not conform with the philosophy and purposes of
the Corporation. Accordingly, land shall not be sold except in
accordance with the following guidelines.
\begin{enumerate}[a.]
\item A parcel of land may be sold pursuant to a resolution adopted by
  an affirmative vote by at least two thirds of the entire Board of
  Directors at a regular or special Board meeting, provided that (i)
  the Corporation has owned the parcel for no more than sixty (60)
  days at the time the vote is taken, (ii) the parcel is not leased to
  any party, and (iii) the resolution states that the location or
  character of the parcel is determined to be such that the charitable
  purposes of the Corporation are best served by selling the land and
  applying the proceeds to the support of other activities serving
  those purposes.
\item In all other circumstances a parcel of land may be sold only with:
  \begin{enumerate}[(1)]
    \item An affirmative vote by at least two thirds of the entire
      Board of Directors at a regular or special Board meeting,
      provided that written notice of such meeting has described the
      proposed sale and the reasons for the proposal; and
    \item The approval of two thirds of the Regular Members present at
      a regular or special Membership Meeting, a quorum being
      assembled, provided that written notice of such meeting has
      described the proposed sale and the reasons for the proposal.
  \end{enumerate}
  \item If any of the Corporation's land is to be sold to any person
    or entity other than a not-for-profit corporation or public agency
    sharing the purposes of the CLT, any ground lessees on that land
    shall have the opportunity to exercise a right of first refusal to
    purchase the land that they have been leasing from the CLT.
\end{enumerate}

