\section{Special Districts and Stewardship by Subsidiary}
\noindent
It is a purpose of the Corporation to facilitate the empowerment of
residents through the control and management of land in their
locale. Accordingly, where the interest of residents is sufficient, a
Special District may be established along with the establishment of a
Subsidiary of the Corporation, for the purpose of independently
managing some or all of the land holdings of the Corporation within
the Special District.

\subsection{Boundaries}
Special Districts will be non-overlapping and will coincide with the
boundaries of any neighborhood or contiguous group of neighborhoods
within the City of Rochester, NY.

\subsection{Incorporation and Dissolution}
The designation or removal of a Special District and the incorporation
or dissolution of an associated Subsidiary will require:
\begin{enumerate}[a.]
  \item An affirmative vote by at least two thirds of the entire Board
    of Directors at any regular or special Board meeting, provided
    that written notice of such meeting has set forth the proposed
    incorporation or dissolution with an explanation thereof; and
  \item An affirmative vote by at least two thirds of the Regular
    Members present at any regular or special Membership meeting, a
    quorum being assembled, provided that written notice of such
    meeting has set forth the proposed incorporation or dissolution
    with an explanation thereof.
\end{enumerate}

\subsection{Similar Structure}
The structure of any Special District Subsidiary must be similar to
that of the Corporation with respect to purposes, membership classes,
member rights, partitioning of the board of directors, operational
transparency, and conflicts-of-interest policy.

\subsection{Oversight}
It is the responsibility of the Board of Directors to review the
structure, policies, finances, and operations of each Subsidiary at
least annually and decide whether they are satisfactory.

\subsection{Transfer of Membership}
Any member of a Special District Subsidiary will automatically be a
Member of the Corporation, of the corresponding membership
class. Membership dues to the Corporation may be paid directly by the
Subsidiary on behalf of its members.

\subsection{Transfer of Land}
Land located within the associated Special District may be transferred
or leased to a Subsidiary by decision of the Board of Directors. The
Corporation will accept title and stewardship of land relinquished by
the Subsidiary. A Subsidiary may not sell land.

